### 2016-03-13 paper/stereo.tex

\section{Swarm Fusion instantiation}
We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantity the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}. For some problems, we
have further limited the capabilities of SF on purpose, to enable
effective and fair comparative evaluations. We now explain the details
of the three problems.

@@

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average robust photoconsistancy
score~\cite{woodford} between the reference image and the others inside a $7\times 7$
pixels window.
\begin{equation}
  \text{\hang{equation to fill in}}
\end{equation}
Pairwise terms are simple truncated absolute label
difference with maximum label difference $\sigma_s=4$. The total energy is
defined by the sum of the two, while scaling the pairwise term by a
factor of $0.005$. For simplicity we don't enforce visibility constraint.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it
slow due to the overhead.\hang{Don't quite understand this
  sentence. Does the ``dominant'' means running time or energy? In my
  experiments, unary terms are pre-computed and are not counted into
  the running time} Therefore, we have chosen Parallel Alpha
Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

Since the optimization in the above stereo problem is fairly easy, we
compare our method with standard sequential alpha expansion, parallel
alpha expansion \cite{first_fusion_viktor} and hierarchy fusion
\cite{olga}. In all experiment, we use $\alpha$-expansion to fuse
single label proposals, and QPBO to fuse multi-label proposals.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
solution proposal in one step and a neighboring solution in the
next. For standard SF, we have used ($\alpha=1, \beta=1$).

after 4 iterations (alpha, beta),

>>>>

\section{Swarm Fusion instantiation}
We compare SF against competing approaches over three problems in
Computer Vision. SF framework has high degrees of freedom and the
challenge is to properly quantify the contributions of various
algorithmic aspects. For this purpose, we have used the three SF
architectures illustrated in Fig.~\ref{fig:model}. For some problems,
we have further limited the capabilities of SF on purpose, to enable
effective and fair comparative evaluations. We now explain the details
of the three problems.

@@

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this
stereo represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average robust photoconsistancy
score~\cite{woodford} between the reference image and the others
inside a $7\times 7$ pixels window.  Pairwise terms are simple
truncated absolute label difference with maximum label difference
$\sigma_s=4$. The total energy is defined by the sum of the two, while
scaling the pairwise term by a factor of $0.005$. For simplicity we
don't enforce visibility constraint.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it
slow due to the overhead.\hang{Don't quite understand this
  sentence. Does the ``dominant'' means running time or energy? In my
  experiments, unary terms are pre-computed and are not counted into
  the running time} Therefore, we have chosen standard sequential
$\alpha$-expansion, Parallel Alpha Expansion(PAE)~\cite{delong} and
Hierarchical Fusion~\cite{delong,olga} with graph-cuts optimization as
the competing methods.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set
to 4. In this case one thread will fuse 4 labels by TRW-S per
iteration and never exchanges solutions with other threads. SF-MF
implies $\alpha+\beta=1$, where each thread will expand 3 labels
(repeat $\alpha=1, \beta=0$ for 3 iterations) and then fuse one
solution from other threads ($\alpha=0, \beta=1$) by QPBO. In the later
case, a thread randomly chooses one target thread to grab solution
from. For standard SF, we have used ($\alpha=4, \beta=1$). For the
SF-SS architecture, we performed a final fuse of solutions from all
thread by multiway fusion.
